% =============================================================================
% Claude for Financial Services — what it is, and where we stand
% Beamer deck (Metropolis theme), 16:9
%
% Compile:
%   latexmk -pdf -xelatex claude-financial-services.tex
% =============================================================================
\documentclass[11pt,aspectratio=169]{beamer}

% --- Theme -------------------------------------------------------------------
\usetheme{metropolis}
\metroset{
  progressbar=frametitle,
  numbering=fraction,
  block=fill,
  sectionpage=progressbar,
  subsectionpage=progressbar
}

% --- Encoding & fonts --------------------------------------------------------
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{fontspec}

% --- Colour palette ----------------------------------------------------------
\definecolor{accentpurple}{HTML}{7C3AED}
\definecolor{darkgray}{HTML}{1F2937}
\definecolor{lightgray}{HTML}{F3F4F6}
\definecolor{successgreen}{HTML}{059669}
\definecolor{warningred}{HTML}{DC2626}
\setbeamercolor{progress bar}{fg=accentpurple}
\setbeamercolor{frametitle}{bg=darkgray}
\setbeamercolor{title separator}{fg=accentpurple}

% --- Tables / graphics / code ------------------------------------------------
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\lstdefinestyle{prompt}{
  basicstyle=\ttfamily\footnotesize,
  backgroundcolor=\color{lightgray},
  frame=none,
  xleftmargin=10pt,
  framexleftmargin=10pt,
  breaklines=true,
  showstringspaces=false,
}
\lstset{style=prompt}

% hyperref is auto-loaded by beamer; just configure it here to avoid option clash
\hypersetup{hidelinks}

% --- Custom commands ---------------------------------------------------------
\newcommand{\good}{\textcolor{successgreen}{\checkmark}}
\newcommand{\bad}{\textcolor{warningred}{\textbf{\texttimes}}}
\newcommand{\hl}[1]{\textbf{\textcolor{accentpurple}{#1}}}

% --- Title -------------------------------------------------------------------
\title{Claude for Financial Services}
\subtitle{What it is, and where we stand}
\author{Internal briefing}
\institute{Informational --- no procurement ask}
\date{June 2026}

% =============================================================================
\begin{document}

\maketitle

% =============================================================================
\begin{frame}{What this deck is --- and isn't}
  \textbf{Is:}
  \begin{itemize}
    \item An honest account of what Claude for Financial Services is
    \item A clear statement of what we can and cannot do with it today
    \item Pragmatic guidance for working well with what we have
  \end{itemize}
  \vfill
  \textbf{Isn't:}
  \begin{itemize}
    \item A procurement ask
    \item A criticism of M365 Copilot
    \item Encouragement to use personal Claude accounts for office work
  \end{itemize}
\end{frame}

% =============================================================================
\section{What it is}

\begin{frame}{The headline}
  On \hl{5 May 2026}, Anthropic launched Claude for Financial Services:
  \begin{itemize}
    \item \textbf{10 ready-to-run agent templates} for high-volume FS work
    \item \textbf{Deep integration with Microsoft 365} (Excel, PowerPoint, Word, Outlook)
    \item \textbf{MCP-based connectors} to $\sim$11 financial data providers
    \item \textbf{Enterprise controls}: SSO, SCIM, audit logs, ISO/IEC 42001:2023
  \end{itemize}

  \vfill
  Underlying model: \hl{Claude Opus 4.7} --- leads Vals AI Finance Agent benchmark at \hl{64.37\%}.
\end{frame}

\begin{frame}{The 10 agent templates}
  \centering\footnotesize
  \begin{tabular}{lp{0.6\textwidth}}
    \toprule
    \multicolumn{2}{l}{\textit{Research \& Client Coverage}} \\
    \midrule
    Pitch Builder       & Target lists $\rightarrow$ comps $\rightarrow$ pitchbook + cover note \\
    Meeting Preparer    & Client / counterparty briefs ahead of calls \\
    Earnings Reviewer   & Transcripts + filings $\rightarrow$ model updates + flagged changes \\
    Model Builder       & Builds models from filings, feeds, analyst inputs \\
    Market Researcher   & Sector / issuer tracking; news + filings + broker synthesis \\
    \midrule
    \multicolumn{2}{l}{\textit{Finance \& Operations}} \\
    \midrule
    Valuation Reviewer  & Checks valuations vs comparables and firm standards \\
    GL Reconciler       & Reconciles GL accounts; NAV calculations \\
    Month-End Closer    & Close checklist, journal entries, close reports \\
    Statement Auditor   & Statement consistency and audit-readiness review \\
    KYC Screener        & Assembles entity files, packages escalations \\
    \bottomrule
  \end{tabular}
\end{frame}

\begin{frame}{How each template is built}
  Each template is a \hl{bundle of three layers}:

  \medskip
  \begin{enumerate}
    \item \textbf{Skills} --- markdown instructions and domain knowledge (\textit{``how a senior banker does this'', written down})
    \item \textbf{Connectors} --- governed MCP access to data (Daloopa, FactSet, S\&P, Moody's, \ldots)
    \item \textbf{Subagents} --- specialised Claude models the main agent calls for sub-tasks
  \end{enumerate}

  \vfill
  Design innovation: \hl{skills are inspectable markdown, connectors are scoped, subagents are addressable}. Not a black box.
\end{frame}

\begin{frame}{Microsoft 365 integration}
  This is the overlap with our existing M365 Copilot.

  \medskip
  \centering\small
  \begin{tabular}{lp{0.55\textwidth}}
    \toprule
    \textbf{App} & \textbf{What Claude does} \\
    \midrule
    Excel       & Builds models from filings + data feeds; audits formulas; sensitivities \\
    PowerPoint  & Drafts decks that auto-update when numbers change \\
    Word        & Edits credit memos against firm templates \\
    Outlook     & Drafts cover notes for pitchbooks \\
    \bottomrule
  \end{tabular}

  \vfill
  \raggedright Independent benchmark: \hl{83\%} on complex Excel tasks (Financial Modeling World Cup, via FundamentalLabs).
\end{frame}

\begin{frame}{Data connectors}
  MCP-based, governed, scoped, auditable:

  \vfill
  \centering
  Daloopa $\cdot$ Morningstar $\cdot$ S\&P Global $\cdot$ FactSet $\cdot$ Moody's
  \medskip\\
  MT Newswires $\cdot$ Aiera $\cdot$ LSEG $\cdot$ PitchBook $\cdot$ Chronograph $\cdot$ Egnyte

  \vfill
  \raggedright
  Not a model scraping the web. \hl{Governed, auditable connections} --- the form of integration regulated firms actually need.
\end{frame}

% =============================================================================
\section{How it ships}

\begin{frame}{Three access paths}
  \centering\small
  \begin{tabular}{lp{0.35\textwidth}p{0.32\textwidth}}
    \toprule
    \textbf{Path} & \textbf{What you get} & \textbf{Requires} \\
    \midrule
    A. M365 + Cowork     & The polished, in-the-flow path & Claude Team / Enterprise + M365 plugin install \\
    B. Claude Code       & Developer-facing terminal flow & Claude Code subscription \\
    C. Managed Agents    & Programmatic, autonomous & Org Anthropic API + engineering \\
    \bottomrule
  \end{tabular}
\end{frame}

% =============================================================================
\section{Where we stand}

\begin{frame}{What we have --- and don't}
  \begin{columns}[T,onlytextwidth]
    \begin{column}{0.46\textwidth}
      \textbf{Have} \medskip
      \begin{itemize}
        \item \good\ Microsoft 365 Copilot
        \item \good\ GitHub Copilot
      \end{itemize}
      \medskip
      \footnotesize\textit{The full list of sanctioned office AI tooling.}
    \end{column}
    \begin{column}{0.5\textwidth}
      \textbf{Don't have} \medskip
      \begin{itemize}
        \footnotesize
        \item \bad\ Claude.ai (consumer)
        \item \bad\ Claude Team / Enterprise
        \item \bad\ Claude for M365 plugin
        \item \bad\ Claude Cowork
        \item \bad\ Claude Code
        \item \bad\ Anthropic API (org-level)
      \end{itemize}
    \end{column}
  \end{columns}

  \vfill
  \hl{No path} from M365 Copilot or GitHub Copilot to the Claude FS agents. The two product families are separate.
\end{frame}

\begin{frame}{On personal accounts}
  Some of us hold personal Claude subscriptions. Important boundary:

  \vfill
  \begin{exampleblock}{}
    A personal account is \hl{not a sanctioned channel for office work}.
    \medskip
    \begin{itemize}
      \item No DPA with our firm.
      \item No audit logging into our compliance posture.
      \item Default Anthropic retention (not enterprise zero-retention).
    \end{itemize}
    \medskip
    \textbf{Personal Claude is for personal exploration. Office work goes through office-sanctioned tools.}
  \end{exampleblock}

  \vfill
  This is true regardless of how useful the output looks.
\end{frame}

\begin{frame}{What we are NOT saying --- and what we ARE}
  \begin{columns}[T,onlytextwidth]
    \begin{column}{0.48\textwidth}
      \textbf{NOT} \medskip
      \footnotesize
      \begin{enumerate}
        \item \textbf{Not} that M365 Copilot is bad. Strong for FS work inside M365 surfaces.
        \item \textbf{Not} that Claude is necessarily better. Different shapes; comparison is task-dependent.
        \item \textbf{Not} lobbying for procurement. Informational only.
        \item \textbf{Not} encouraging personal-account workarounds.
      \end{enumerate}
    \end{column}
    \begin{column}{0.48\textwidth}
      \textbf{ARE} \medskip
      \footnotesize
      \begin{enumerate}
        \item The Claude FS offering is real, well-engineered, relevant to our discipline.
        \item We don't have access through any office channel today.
        \item Understanding what it is helps us make informed tooling judgements.
      \end{enumerate}
    \end{column}
  \end{columns}
\end{frame}

% =============================================================================
\section{What we can do today}

\begin{frame}{Where M365 Copilot earns its keep for FS}
  \centering\small
  \begin{tabular}{lp{0.45\textwidth}}
    \toprule
    \textbf{Task} & \textbf{Why it works} \\
    \midrule
    Drafting client emails, cover notes & Outlook native context \\
    Summarising Teams meetings & Live transcript + speakers \\
    Summarising SharePoint trees & Native indexing \\
    First-cut models in Excel & Scaffolds from a written spec \\
    Sensitivity on existing models & Vary X by $\pm10\%$, show Y \\
    Drafting dashboard commentary & Reads data, writes narrative \\
    Reconciling vs Dynamics 365 / SAP & If connectors installed \\
    Summarising credit memos in Word & With file open in Word \\
    \bottomrule
  \end{tabular}

  \vfill
  \raggedright \textbf{Pattern}: anything inside M365 that benefits from knowing what's around it.
\end{frame}

\begin{frame}{Where M365 Copilot is weak for FS}
  \centering\small
  \begin{tabular}{lp{0.45\textwidth}}
    \toprule
    \textbf{Task} & \textbf{Why} \\
    \midrule
    Building a model from a filing & Reasonable; complex modelling not its strength \\
    Multi-doc synthesis across 200 pages & Useful context degrades \\
    Source attribution on every claim & Inconsistent \\
    Pulling from FactSet / S\&P / PitchBook & No native connectors \\
    Autonomous multi-step workflows & Requires Copilot Studio build \\
    Complex Excel formula-chain auditing & Improving; below Claude on FMW tasks \\
    \bottomrule
  \end{tabular}

  \vfill
  \raggedright \textbf{Implication}: route the task to the surface that fits. Don't force Copilot into things it's weak at.
\end{frame}

\begin{frame}{What to tell colleagues asking about Claude}
  \begin{exampleblock}{Clean two-sentence version}
    \textit{Yes --- Anthropic launched Claude for Financial Services in May. It's a strong product for our type of work, but we don't have a sanctioned channel to use it: our office AI tooling today is Microsoft 365 Copilot and GitHub Copilot, and Claude requires a separate subscription we haven't acquired.}
  \end{exampleblock}

  \vfill
  \begin{block}{If they push: ``can I just use my personal account?''}
    \textit{Not on office data, no --- that would be a data-handling issue regardless of how useful the output is. Personal Claude is fine for personal exploration; office work goes through office-sanctioned tools.}
  \end{block}
\end{frame}

% =============================================================================
\section{Summary}

\begin{frame}{Summary}
  \begin{itemize}
    \item Claude for Financial Services is \hl{real, polished, relevant} --- 10 FS agents, M365 integration, governed FS data connectors, enterprise controls.
    \item We \hl{don't have access} through any current office channel; M365 Copilot + GitHub Copilot are our tools today.
    \item M365 Copilot is \textbf{well-suited} to a large slice of FS work; route tasks intelligently.
    \item The Anthropic FS repo is \textbf{Apache 2.0} --- worth reading as reference material even without subscription access.
    \item This briefing is \textbf{informational}, not a procurement ask.
  \end{itemize}
\end{frame}

% =============================================================================
\begin{frame}[plain]
  \begin{center}
    {\Huge Thank you}\\[1.2em]
    {\Large Questions?}\\[2.4em]
    \small \textit{Verified June 2026 against anthropic.com / claude.com / github.com/anthropics/financial-services.}
  \end{center}
\end{frame}

\end{document}
